---
title: "Testing"
author: "Andy Beck"
date: "4/22/2019"
output: html_document
---

```{r setup}
knitr::opts_chunk$set(
	message = FALSE,
	warning = FALSE,
	include = TRUE
)
library(Rcpp)
suppressMessages(library(tidyverse))
suppressMessages(library(R.matlab))
```

## AEFFP Testing

The purpose of this document is to verify my ADMM implementation matches that of Stephen Boyd [https://stanford.edu/~boyd/papers/admm/logreg-l1/logreg.html](https://stanford.edu/~boyd/papers/admm/logreg-l1/logreg.html)

## Validating agaist matlab implementation

### Generate Data

* p = 10, 5 non-zero
* X = 200-by-10 matrix of predictors
* y = 200 observations

```{r}
n <- 200
p <- 5
set.seed(815)
beta <- c(rnorm(floor(p/2)), rep(0,ceiling(p/2)))
b0 <- rnorm(1) # random intercept
X <- matrix(rnorm(n*p), nrow = n, ncol = p)
pr <- 1/(1+exp(-X %*% beta + b0))
y = rbinom(n,1,pr)
y <- ifelse(y==1,1,-1)

qplot(as.numeric(y==1), geom = "histogram")
```

Now save the data in format matlab can read:

```{r}
writeMat("input.mat", X=X, y=y)
```

### Run with my implementation

Note: Boyd's implementation uses $m \times \mu$ in place of $\lambda$ for some reason, where m is the number of observations.

```{r}
#sourceCpp("src/lasso_logisticC.cpp")
library(aeffp)
admmlasso_logC(X,y,0.0057 * 200, 1)
```

